\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage[ruled,norelsize]{algorithm2e}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{soul}
\usepackage{url}


\definecolor{javared}{rgb}{0.6,0,0} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc

% ===============================================
% MyJavaSmallStyle
% ===============================================
\lstdefinestyle{MyJavaSmallStyle} {
  language=Java,
  frame=lines,
  xleftmargin=15pt, 
  stepnumber=1, 
  numbers=left, 
  numbersep=5pt,
  stepnumber=1,
  numberstyle=\tiny\bf,%\color[gray]{0.777}, 
  belowcaptionskip=\bigskipamount,
  captionpos=b, 
  escapeinside={*'}{'*},
  tabsize=5,
  emphstyle={\bf},
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\color{javapurple}\bfseries,
  stringstyle=\color{javared},
  commentstyle=\color{javagreen},
  morecomment=[s][\color{javadocblue}]{/**}{*/},
  showspaces=false,
  columns=flexible,
  showstringspaces=false,
  morecomment=[l]{//},
  tabsize=2,
  morekeywords={, Package,Invariant,Field,Where,Assert,ToLc,Split,Msg,Immutable,<<<,eq,neq,not,has,Assert,AssertExists,Attribute,Uc,Lc,},
  breaklines=true
}

\newcommand{\ttt}[1]{\tt\small{#1}}
\newcommand{\tool}{{\ttt CodeAid}}
\lstset{
	% numbers=left,
	% numberstyle=\tiny,
	% backgroundcolor=\color{light-gray},
	basicstyle=\scriptsize\ttfamily,
	breaklines=true,
	breakatwhitespace=true,
	captionpos=b,
	columns=flexible,
	escapeinside={(*@}{@*)},
	frame=tb,
	framerule=0.6pt,
	% xleftmargin=\parindent,	
	% xrightmargin=\parindent,
	language=Java,
	% numbersep=5pt,
	showstringspaces=false
}
\newcommand{\explanation}[1]{
	\parbox{0.45\textwidth}{
		\rule{0.4\textwidth}{0.1pt}
		\vspace*{0.5em} \\
		{#1}
	}
}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
	
	\newcommand\todo[1]{\textcolor{red}{TODO: #1}}
	
	\makeatletter
	\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
	\makeatother
	


%\title{Are co-occurring code fragments useful for code recommendation?}
\title{Towards Searching Beyond Similar Code}
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}


%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%}

\maketitle

\begin{abstract}

Code-to-code search can help developers find similar solutions and identify possible improvement opportunities or alternative choices. 
Existing search tools only recommend other code locations that are syntactically or semantically similar to the given code but do not reason about other kinds of relevant code that a developer should also pay attention to, e.g., an auxiliary function to accomplish a complete task.  
%Though such surrouding, co-occurring code fragments are not similar to the given code query, they might be necessary to work together with the given code to accomplish a complete task or provide auxilary functionality. 
There is also limited understanding about what other kinds of code relevancy may exist in practice beyond code similarity and thus should be incorporated into modern code search engines. 
To bridge the gap, this paper presents an in-depth analysis of other code fragments that co-occur with similar code that a regular search engine typically recommends and their relevance to the given code query.

To this end, we first constructed a large data set of 21K groups of similar code written in Java, using Stack Overflow code snippets as queries and identifying their counterparts in GitHub via clone detection. For more than half of these SO code snippets, their GitHub counterparts share common code that co-occurs in the same Java file yet not similar to the original queries. We manually inspected a random sample of 50 commonly co-occurring code fragments and found 74\% of them represent relevant functionality that should be included in code search results. Furthermore, we identified three major types of relevant co-occurring code---{\em complementary}, {\em supplementary}, and {\em alternative} functions. This study result calls for a new search engine that accounts for such code relevance beyond code similarity.  %the prevalence and usefulness of relevant co-occuring functions. At the end, we implemented a code search tool that incorporates such relevant functions as a possible tool design.

%Recommending related code of a given query can help programmers detect
%situations that they have overlooked, or that they did not know how to solve.
%Existing code-to-code search tools only identify syntactically or semantically
%similar code given a code of interest. These tools focus on the counterparts
%themselves, while ignoring the co-occurring code fragments with the counterpart.


%In this paper, we describe a technique to find and rank co-occurring code
%fragments to a given code query in a code corpus. Specifically, we use GitHub
%Java projects as our corpus and focus on method-level code retrieval. Given a
%code fragment of interest, we use a code clone detection tool to detect all its
%similar counterparts across different GitHub files, and then rank other methods
%in the files based on clustering statistics. We keep the top ranked co-occurring
%methods as related ones.

%In order to evaluate the related code fragments, we use Stack Overflow (SO) code
%snippets as queries, and measure the precision of the retrieved related methods.
%We gather a query code base of 21,207 SO code snippets written in Java. We
%discovered related co-occurring code fragments in GitHub for 11,110 of these
%snippets. We also perform an in-depth analysis on a sample of these related code
%snippets and categorize the relationship between a SO query snippet and related
%code, sheding light on how related code can be useful in practice. We then
%manually evaluate the usefulness of related GitHub code, and get a precision of
%75.6\%. Our results show that top-ranked co-occurring code fragments are useful 
%for the users, and we provide a Chrome extension as one possible implementation
%of recommending related co-occurring code fragments in real life.
\end{abstract}

\begin{IEEEkeywords}
code search, related code, mining software repositories
\end{IEEEkeywords}


\input{intro}
\input{approach}
\input{dataset}
\input{eval}
\input{chrome}
\input{related}


\section{Threats to Validity}
In terms of internal validity, we only investigate the kinds of code relevancy in common, co-occurring code, based on the observation that relevant code may often co-locate in the same file. Though we indeed find interesting types of relevant code by exploiting this proximity property of code, we may miss other kinds of relevant code that is not in the same file. 

In terms of external validity, this work only analyzes code written in one programming language, Java. Previous studies have shown that JavaScript and Python have more clones than Java and C~\cite{lopes2017dejavu, yang2017stack}. Therefore, we are likely to find more common, co-occurring code for JavaScript and Python. In addition,  we may find other kinds of relevant code in those different languages. For instance, Lopes et al.~find that a large portion of code clones in JavaScript are generated from boilerplate~\cite{lopes2017dejavu}. Hence, we may also find that many common, co-occurring code of a JavaScript code fragment is because of boilerplate code.


{\em Limitations.} Given a code query, {\tool} needs to first search a code corpus to find the counterparts of this query and then recommends common, co-occurring code around those counterparts. In this work, we curate a large code corpus of 50K GitHub repositories with at least five stars to ensure that we have a large code corpus to search from. However, if a given code fragment  implements a project-specific logic that is not likely to be found in other projects, {\tool} is unlikely to recommend relevant code of the given code fragment. Though {\tool} currently supports Java, it is not restricted to any programming languages. The Java parser is only used to tokenize code fragments for clone detection and can be substituted with any off-the-shelf parsers of other languages.

%Our approach also inherits the limitations from the clone detector, SourcererCC. It depends on the clone detector to find accurate similar code. However, our approach is not bound with any particular clone detector. With its generality, SourcererCC can be replaced by other code-to-code search engines. 

\section{Conclusion}
\label{sec:conclude}

Code-to-code search engines focuses on retrieving syntactically or semantically similar code fragments to a given query, without considering auxiliary or complementary code that may also be related to the query. The goal of this work is to explore the existence of other kinds of related code beyond similar code, and discuss the usefulness of such related code for recommendation in practice.

Co-occurring code is an interesting start point of exploring related code. We built an automated approach to identify, cluster, and rank common, co-occurring code. From detailed manual evaluation, we found 74\% of our sampled code show valid relevancy to the query, and this relevancy can be categorized into three types--{\em complementary}, {\em supplementary}, and {\em alternative} functionality. Our findings shows the benefit of recommending common-occurring code, beyond similar code. We also implemented a Chrome extension that demonstrates an application of our approach in practice. We experimented to show that other search engines cannot fulfill recommending related code fragments as we proposed. We are planning to perform more user study on our tool in near future.



%For future work, we may try different user-defined query code base and search code corpus to further evaluate {\tool}. For example the search code corpus can be the code base for a company or previous projects from a user. We may import the tool into a Eclipse plugin and help developers during real life programming process. The use scenario will be, when a user is currently writing a code fragment and uses it as query to search {\tool} plug-in, we will return the ranked list of related code from the company's code base or the user's own projects.


\bibliographystyle{plain}

\bibliography{ref}





\end{document}
