\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage[ruled,norelsize]{algorithm2e}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{soul}
\usepackage{url}

\newcommand{\ttt}[1]{\tt\small{#1}}
\newcommand{\tool}{{\ttt CodeAid}}
\lstset{
	% numbers=left,
	% numberstyle=\tiny,
	% backgroundcolor=\color{light-gray},
	basicstyle=\scriptsize\ttfamily,
	breaklines=true,
	breakatwhitespace=true,
	captionpos=b,
	columns=flexible,
	escapeinside={(*@}{@*)},
	frame=tb,
	framerule=0.6pt,
	% xleftmargin=\parindent,
	% xrightmargin=\parindent,
	language=Java,
	% numbersep=5pt,
	showstringspaces=false
}
\newcommand{\explanation}[1]{
	\parbox{0.45\textwidth}{
		\rule{0.4\textwidth}{0.1pt}
		\vspace*{0.5em} \\
		{#1}
	}
}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\newcommand\todo[1]{\textcolor{red}{TODO: #1}}

\makeatletter
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\makeatother


\title{CodeAid: Recommending Related Code
%	\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%}

\maketitle

\begin{abstract}
Finding similar code for a given code query can help programmers
detect situations that they had overlooked, or that they did not know
how to solve. Most code-to-code search tools aim at finding
syntactically or semantically similar code given some code of
interest. We take a different approach to code-to-code search that
recommends relevant {\em auxiliary} or {\em complementary}
code. Such relevant code is not semantically similar to the code
query, but could be important to work together with the
given code to accomplish a complete or related functionality.

In this paper, we describe a code recommendation technique, CodeAid, that returns 
code fragments that are related to a given code query in a code corpus. Specifically, we
use GitHub Java projects as our corpus and focus on method-level code retrieval. 
Given a code fragment of interest, we use a code clone detection tool to detect all its similar
counterparts across different GitHub files, and then recommend other related
methods based on co-occurrence statistics.

In order to evaluate the effectiveness of CodeAid, we use Stack Overflow
(SO) code snippets as queries, and measure the precision of the
retrieved related methods. We gather a query code base of 21,207 SO
 code snippets written in Java. For 11,110 of these snippets, CodeAid discovered related
code fragments in GitHub and recommended to developers. We then manually evaluate 
the relevance of recommended GitHub code. Using this methodology, CodeAid has a
precision of 75.6\%. We also performan an in-depth analysis on a sample of these code snippets
and categorize the relationship between a SO query snippet and recommended code, 
sheding light on how CodeAid can be useful in practice.

\end{abstract}

\begin{IEEEkeywords}
code recommendation, related code, code search, mining software repositories
\end{IEEEkeywords}

\input{intro}
\input{approach}
\input{dataset}
\input{eval}
\input{chrome}
\input{related}


\section{Conclusion}
\label{sec:conclude}

We have presented {\tool}, a code-to-code search technique and tool
that recommends code fragments related to the code query. The
information need that underlies the design of {\tool} is different
from that of traditional code search engines: rather than retrieving
similar code, it retrieves code within the functionality family of the
code query. This broader context allows programmers to be aware of
related code that may be useful when developing their own
functions. {\tool} works by analyzing co-occurrences of code fragments
in very large code bases, such as GitHub projects, and then clustering
those potential matches for a given code query.

We evaluated {\tool} using a large dataset of code queries collected
from Stack Overflow snippets, and a very large code base of Java
projects collected from GitHub. The evaluation shows that {\tool} is
able to find related fragments for 52.4\% of the queries. A closer look at a set of 30
queries shows that {\tool} has a good precision of 75.6\%. This is
a promising result for a new approach to code search. 

One limitation of {\tool} is that the recommendation power of {\tool} strongly correlates with the similarity behavior of the dataset. To retrieve related code fragments, {\tool} requires the query code to have similar counterparts in the search query corpus; it also asks for similar method pairs within search query corpus itself. 

For future work, we may try different user-defined query code base and search code corpus to further evaluate {\tool}. For example the search code corpus can be the code base for a company or previous projects from a user. We may import the tool into a Eclipse plugin and help developers during real life programming process. The use scenario will be, when a user is currently writing a code fragment and uses it as query to search {\tool} plug-in, we will return the ranked list of related code from the company's code base or the user's own projects.

%\section*{References}

\bibliographystyle{plain}

\bibliography{ref}

\end{document}
